### 2019-06-15 papers/journal/intro.tex
First Update for revision

\noindent A characteristic feature of eukaryotic cells is the presence of multiple internal membrane-bounded compartments. 
%
These compartments exchange molecules amongst themselves in small membrane-bounded packets called vesicles~\cite{alberts2002molecular}. 
%
The molecular interaction network that controls the vesicle traffic system involves dozens of varieties of molecules that regulate the flow of cargo. 
%
Due to this, obtaining a complete understanding of the vesicle transport system through physical experimentation alone is a hard problem.
%
Highly reduced models of vesicle traffic have previously provided insight into how the chemical composition of various cellular compartments can emerge out of molecular regulation and cargo flow. 
%
However, the high complexity of problems in VTS restricts the use of traditional methods like simulation and statistical reasoning~\cite{mani2016stacking}. 
%The high complexity of problem restricts the use of traditional methods like simulation and statistical reasoning and the requirement of precise analysis makes formal methods an ideal candidate. 
In this paper, using formal methods, we solve the problem of completing incomplete VTS graphs while also considering constraints due to molecular interactions, thereby demonstrating the effectiveness of such methods.
%
The phenomenology of vesicle traffic is unlikely to be familiar to many readers; however, the details are important for the rest of our discussion. 
%
Therefore, we give an overview of the molecular mechanism of the VTS and then we sketch out a few interesting problems that are key to an understanding of the VTS.
%
\subsection{Vesicle traffic system}
%Vesicles were discovered decades ago, in the early 1950s, and s
\noindent The major molecules involved in the vesicle traffic system~\cite{wells2005discovery} can roughly be categorized as budding molecules, whose role is in the formation and budding of transport vesicles from the source compartment, and fusion molecules, which enable fusion of transport vesicles with the target compartments. 
%
Below, we give a brief description of the sequence of steps involved in the vesicle transport process. 
%
Through this description, we wish to provide a glimpse of the kind of molecular regulatory interactions that we encode in our model.

\begin{figure}
	\includegraphics[height=10cm,width=12cm]{diavts.eps}
	\caption{Schematic of the vesicle transport system. Steps involved in vesicle transport between two compartments: a source and a target compartment are shown. 
	%
	The symbols used for different molecules involved in vesicle traffic are explained in the key. At the source compartment, transmembrane cargo proteins are sorted by cytosolic adaptor proteins. 
	%
	Here, different colours indicate different types of cargo and adaptor proteins. Coat proteins are recruited to the forming vesicle by adaptor proteins. 
	%
	Note here that a single type of coat protein can interact with multiple types of adaptor proteins. Subsequently, the vesicle is pinched off at its neck, for example by dynamin. 
	%
	Once the vesicle has left the source compartment, the coat and adaptor proteins fall off and the vesicle is recognized and bound by a tethering complex which is linked to the target compartment. 
	%
	At the target compartment, the tethered vesicle undergoes fusion, thereby releasing its contents.}
    \label{fig:vts}
\end{figure}

\subsubsection{Vesicle budding} The process of vesicle budding involves sorting and packaging of cargo molecules, membrane deformation and budding of the vesicle from the source compartment (Figure~\ref{fig:vts}).
%
Cargo sorting is performed by cytosolic adaptor proteins. 
Adaptors are recruited to the source compartment through interactions with the lipids that form the compartment's membrane, and interactions with molecular switches called Arf/Sar which signal the initiation of vesicle formation~\cite{paczkowski2015cargo}. 
%
Then these adaptors bind to cargo molecules and thereby sequester them for packaging. 
%
Different adaptor proteins act at different compartments, for example, vesicle formation at the ER requires the adaptor sec23/24, and the AP2 adaptor is used for packaging vesicles at the plasma membrane.
%

@@

\subsubsection{Vesicle fusion} The process of vesicle fusion involves two steps recognition of the correct target compartment and fusion of the transport vesicle (Figure~\ref{fig:vts}).

@@

%\somya{schematic of intracellular compartments and  major routes}
\subsubsection{Major paths in the vesicle transport network}
Molecules traverse the cell in a series of vesicles, and there are two major routes of vesicle transport in all eukaryotic cells.
%
\begin{itemize}
	\item The secretory route takes proteins from the ER (their site of production) to the plasma membrane( from where they are secreted out of the cell) via the Golgi apparatus~\cite{alberts2002molecular}.
	%
	\item The endocytic route takes proteins from the outside of the cell, through the plasma membrane, to the endocytic compartments and the lysosome where they are digested. 
\end{itemize}
Other paths are used for cross talk between the secretory and the endocytic routes. For example, vesicles are sent back and forth between the Trans-Golgi network (secretory route) to the early and the late endosomes (endocytic route)~\cite{progida2016bidirectional}. Also, recently, unconventional vesicle-mediated secretory routes have been found, which bypass the Golgi apparatus. The molecules involved in these routes are as yet unknown~\cite{nickel2018unconventional}. 
%
%\begin{table}
%	\begin{center}
%		\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
%			\hline
%			Nodes & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 \\ \hline
%			Graphs & 0 & 0 & 0 & 1 & 2 & 15 & 121 & 2159 & 68715 & 3952378 \\ 
%			\hline
%		\end{tabular}
%		\label{tab:threec}
%		\caption{Number of simple 3-edge-connected unlabelled N-node graphs.}
%	\end{center}	
%\end{table}

@@

%\ankit{We need not specify Synthesis here. Only connectivity use next subsection to build this.}
%\somya{But this is the para where we explain why connectivity is interesting an biological property}
%\ankit{Yes; Both of our remark looks correct!}
The vesicle transport graphs available today for eukaryotic organisms are incomplete themselves. 
%
In this situation, we use our result as a tool to predict missing edges which satisfy the graph connectivity constraint. 
%
These predictions are intended to be used as guides for future experiments. 
%
A mismatch between our predictions and experiments would indicate that our current understanding of the VTS molecules is necessarily incomplete. 
%
Note that, on the other hand, if our predictions are experimentally confirmed, it does not imply that our understanding of the VTS is complete.\\
%
%\begin{table}[!t]
%	\caption{Table Caption}
%	\label{tab1}
%	\centering
%	{\setlength\tabcolsep{0.1pt}%
%		\begin{tabular}{ccccccccccccccc}
%			& $D_1$ & $D_2$ & $D_3$ & $D_4$ & $D_5$ & $D_6$ && & $D_1$ & $D_2$ & $D_3$ & $D_4$ & $D_5$ & $D_6$ \\
%			$D_1$ & & \cca{0} & \cca{0} & \cca{0} & \cca{2} & \cca{0} && $D_1$ && \cca{0} & \cca{0} & \cca{2} & \cca{2} & \cca{2} \\
%			$D_2$ & \cca{0} & & \cca{2} & \cca{0} & \cca{2} & \cca{0} && $D_2$ & \cca{0} &  & \cca{3} & \cca{0} & \cca{0} & \cca{2} \\
%			$D_3$ & \cca{7} & \cca{4} &  & \cca{3} & \cca{0} & \cca{4} && $D_3$ & \cca{0} & \cca{4} &  & \cca{4} & \cca{2} & \cca{0} \\
%			$D_4$ & \cca{3} & \cca{0} & \cca{7} &  & \cca{4} & \cca{0} && $D_4$ & \cca{0} & \cca{0} & \cca{5} &  & \cca{0} & \cca{0} \\
%			$D_5$ & \cca{3} & \cca{7} & \cca{7} & \cca{2} &  & \cca{4} && $D_5$ & \cca{2} & \cca{2} & \cca{0} & \cca{4} &  & \cca{4} \\
%			$D_6$ & \cca{2} & \cca{2} & \cca{7} & \cca{2} & \cca{6} &  && $D_6$ & \cca{2} & \cca{2} & \cca{3} & \cca{0} & \cca{4} & \\
%	\end{tabular}}
%\end{table}
%
\vspace{-0.5cm}
\begin{example}
%
In Figure~\ref{fig:M1}, we present a VTS that has 2 compartments and 18 molecules with its corresponding pairing matrix.
%
%Molecules are represented as $Q_{i}$'s or $R_{i}$'s to make a clear distinction between Q and R SNAREs.
%
In the VTS, labels are a string of molecule, where we show active molecules in red color.
%
The activity of the molecules on the node is controlled
by the presence of the other molecules (exact Boolean function is not shown). 
%
The activity of the molecules on an edge is determined by the corresponding pairing matrix.
%
Note that molecules $X$ and $Y$ do not take part in the fusion but play a part in determining activity at the corresponding nodes.
%
Below the VTS, we show the pairing matrix.
%
Rows in the matrix correspond to the labels of edges, and columns correspond to the labels of nodes.
%
An entry 1 represents pairing between molecules and 0 represents no pairing.
%
Every molecule flows on a cycle, ensuring steady state.
%
This is a 4-connected graph.
\end{example}
%
\input{pm-1-matrix}
%\subsection{Modeling and Symbolic Analysis of VTS: An Overview}
\label{subsec:graphmodel}
%
\subsection{Combinatorial problem and use of Formal methods}
\noindent The analysis of vesicle traffic systems is a difficult problem
because of the combinatorial scaling of possible traffic topologies and regulatory rules. 
%
%For example, we might want to check some conjecture of interest for all graphs of a certain structure. 
%
%If the analysis is done on a large number of graphs, the joined effect of large quantity of graphs and combinatorially many possible regulatory rules will be difficult to handle by any tool.
If the analysis is done on a large number of graphs, the joined effect of this with combinatorially many possible regulatory rules will be difficult to handle by any tool.
%
Precise analysis of the properties of the VTS would be hindered by the same reason.

@@

\subsubsection{Size of the VTS system}
Let us discuss the rough sizes of the system and expected behaviors.
%%
%A typical VTS may have about 10 compartments.
%%
%%Across eukaryotes, there are 20 broad SNARE varieties, though individual species can
%%contain higher numbers (humans have 41)~\cite{kloepper2007elaborate}..
%%
%The VTS may transport a large number of molecules but the molecules that
%are relevant of the control of VTS are about 50~\cite{kloepper2007elaborate}.
%%
%According to the definition the activity of molecules can be controlled by
%the presence of all other molecules.
%%
%However, in practice the activity of a molecule is controlled by
%the presence of ~2-3 other molecules.
A typical eukaryotic cell contains 9 organelles; the ER, the cis-, medial- and trans-Golgi, the early, late and recycling endosomes, the lysosome and the plasma membrane~\cite{lodish2008molecular}. 
%
The organellar content of cells varies across different organisms, for example, parasitic cells such as Trypanosomes have specialized secretory organelles called rhoptries and micronemes~\cite{gubbels2012evolution}. 
%
The organellar content may also vary across different states of the same cell, for e.g., during cell division, the Golgi apparatus disintegrates into vesicles~\cite{tang2013cell}. 
%
Also, across different cell-types, these organelles may be more or less differentiated, for example, the number of stacks in the Golgi varies across different cells~\cite{polishchuk2004structural}. 
%

@@

% i.e., formally as a boolean function that given requisite labels of nodes and vesicles that returns true if the required regulations are met. 
%
%
% Note that the formulas define among other things constraints over
% paths between nodes in the graph model of VTS. Similarly, one can
% define fusion rules as constraints over the boolean functions modeling
% the regulations.  
% For example, the steady state condition, described informally earlier, can be defined by the formula shown in Listing~1.1.
%\begin{itemize}
%\item \srivas{Detailed BIO to Graph problem}
%\end{itemize}
%Given definitions of fusion and budding rules and the steady state conditions, whether a VTS meets maximum connectivity requirement, i.e. the LGC property, can be verified by checking if the formula show in Listing~1.2 is valid.  Here we have defined the property by checking over existence of any fusion/budding rules.  We can eliminate the existential quantifier if we are interested in checking the property for a particular fusion/budding rule.
%
%\subsection{Converting the Graph Problem into Boolean SAT problem}
%\label{subsec:satproblem}
%To convert the graph problem described in sec~\ref{subsec:graphmodeling}, into a boolean SAT problem, we need to define a scheme to represent graphs and boolean functions using a suitable set of propositional variables.  In our earlier work, we modeled the graph problem in C using arrays to model graphs and boolean function.  We then used the CBMC model checker to convert the graph problem into a SAT problem.  One of the challenges we had in our earlier work is dealing with quantifiers.  Note that the connectedness property defined in Listing~1.2 has quantifier alternation.  Even if we were to eliminate the existential quantifier by instantiating the problem for a fixed set of fusion rules, we would have embedded quantifiers in the antecedent of implications.   CBMC supports only a quantifier-free logic n its assertion language.  In our earlier work we used a combination of explicit enumeration at the C-level and clever use f non-determinism to eliminate alternation of quantifiers.  This enumeration was one source of bottleneck for scaling in our earlier work.  In the current work we eliminate this bottleneck by modeling the problem directly as a SAT instance using uninterpreted functions and recursive relations.  The details of te hnew encding will described in subsequent sections.
%A VTS is {\em $k$-connected} if every pair of compartments remain reachable after dropping $k-1$ vesicles.
%
%This property of VTSs has been considered informative and studied by~\cite{shukla}.
%
%Here we have build an {\em efficient} tool that studies properties of VTSs that are not $k$-connected, from some $k$. 
\subsection{Synthesis of VTS }
\noindent The current picture of the vesicle transport network is far from complete; we do not yet know how many of the cellular proteins reach their resident compartments within the cell, and new vesicle routes are being discovered every year~\cite{nickel2018unconventional,weill2018toolbox}. 
%
Completing the vesicle traffic network is a difficult task for the many important reasons: 
\begin{enumerate}
    \item The core vesicle transport network is conserved across eukaryotes, the traffic network in different organisms~\cite{richardson2015evolutionary,nishimoto2009differential,barlow2017seeing}, and even in different cell types within an organism can be different~\cite{stoops2014trafficking,zhou2015arp2}.

@@

    \item Molecules can have redundant routes within the cell~\cite{shimizu2014compensatory,nakatsukasa2014nutrient}.
    \item Behaviour of traffic molecules in vitro is different from their behavior inside cells~\cite{furukawa2014multiple}.

    \item It can be difficult to distinguish between the direct and indirect effects of experiments involving knock-downs or knockouts of traffic molecules \cite{hirst2004epsinr,mishev2013small}.
\end{enumerate}

Nonetheless, completing the vesicle traffic network for different organisms is very useful. 
%
Many diseases are caused by the malfunction of the vesicle traffic network. 
%
Knowledge of the complete network would be helpful in identifying the root causes of ~\cite{bexiga2013human,gissen2007cargos}. 
%
At a more basic level, having complete pictures of the vesicle traffic system for various organisms and various cell-types would allow comparative studies, and therefore would allow the deduction of modes of evolution of the form of the traffic network. 
%
This would also allow us to decipher features such as parts of the traffic system that is unchanging, and therefore likely to be its core, and parts that are more plastic \cite{barlow2017seeing}.

%\subsection{Synthesis of VTS:}
%
The set of basic constraints the VTS should follow is dictated by underlying cell biology.   
%
In order to attempt to complete a given partial VTS, we have to first agree on the properties that every complete VTS should follow in spite of the basic constraints. 
%
We can use our stability and k-connectivity constraints as a basis for this investigation.   
%
The incomplete VTS might not respect these constraints. 
%
In this paper, using constraints on global vesicle traffic network topology due to local molecular interactions, we take incomplete pictures of vesicle traffic networks as inputs.
%
We output various completed versions of VTS against these properties which can then be tested experimentally.
%
\begin{example}
	%
    In Figure~\ref{fig:synth-vts1}, we present a partial input VTS that has 3 compartments. Figure~\ref{fig:synth-vts2} present it's complete output VTS. 
    %
    The synthesis is performed against the steady state property and 3-connectivity. 
    %The tags PM, EE, and LE represent the corresponding nodes (please refer to Appendix~\ref{sec:ex-vts} for a proper discussion about the nodes and molecules depicted in the diagram). 
    %
    Synthesized edge is in red color and synthesized molecules are presented in blue.
    %
    The synthesis adds one edge and 7 molecules to complete the partial VTS.
    %
    For the sake of clarity, we have not presented the activity of molecules, the corresponding pairing matrix and remaining molecules on the nodes.

\end{example}
\input{synth-dia}

We have implemented the encoding in a flexible tool, which can handle a wide range of synthesis queries. 
%
We have applied our tool on several VTSs including
two found-in-nature VTSs.
%
Our experiments suggest that some of the synthesis problems are solvable by modern solvers and the synthesis technology may be useful for biological research.
%

>>>>

\noindent A characteristic feature of eukaryotic cells is the presence of multiple internal membrane-bounded compartments. 
%
These compartments exchange molecules amo\-ngst themselves in small membrane-bounded packets called vesicles~\cite{alberts2002molecular}. 
%
The molecular interaction network that controls the vesicle traffic system involves dozens of varieties of molecules that regulate the flow of cargo. 
%
Due to this, obtaining a complete understanding of the VTS through physical experimentation alone is a hard problem.
%
Highly reduced models of vesicle traffic have previously provided insight into how the chemical composition of various cellular compartments can emerge out of molecular regulation and cargo flow. 
%
However, the high complexity of problems in VTS restricts the use of traditional methods like simulation and statistical reasoning~\cite{mani2016stacking}. 
%The high complexity of problem restricts the use of traditional methods like simulation and statistical reasoning and the requirement of precise analysis makes formal methods an ideal candidate. 
In this paper, using formal methods, we solve the problem of completing incomplete VTS graphs while also considering constraints due to molecular interactions, thereby demonstrating the effectiveness of such methods.
%
The phenomenology of vesicle traffic is unlikely to be familiar to many readers; however, the details are important for the rest of our discussion. 
%
Therefore, we give an overview of the molecular mechanism of the VTS and then we sketch out a few interesting problems that are key to an understanding of the VTS.
%
%\vspace{-0.5cm}
\subsection{Vesicle traffic system}
%Vesicles were discovered decades ago, in the early 1950s, and s
\noindent The major molecules involved in the VTS~\cite{wells2005discovery} can roughly be categorized as budding molecules, whose role is in the formation and budding of transport vesicles from the source compartment, and fusion molecules, which enable fusion of transport vesicles with the target compartments. 
%
Below, we give a brief description of the sequence of steps involved in the vesicle transport process. 
%
Through this description, we wish to provide a glimpse of the kind of molecular regulatory interactions that we encode in our model.

\begin{figure}
  \begin{center}

	\includegraphics[height=10cm,width=12cm]{fig1.eps}
	\end{center}

	\caption{Schematic of the VTS. Steps involved in vesicle transport between two compartments: a source and a target compartment are shown. 
	%
	The symbols used for different molecules involved in vesicle traffic are explained in the key. At the source compartment, transmembrane cargo proteins are sorted by cytosolic adaptor proteins. 
	%
	Here, different colours indicate different types of cargo and adaptor proteins. Coat proteins are recruited to the forming vesicle by adaptor proteins. 
	%
	Note here that a single type of coat protein can interact with multiple types of adaptor proteins. Subsequently, the vesicle is pinched off at its neck, for example by dynamin. 
	%
	Once the vesicle has left the source compartment, the coat and adaptor proteins fall off and the vesicle is recognized and bound by a tethering complex which is linked to the target compartment. 
	%
	At the target compartment, the tethered vesicle undergoes fusion, thereby releasing its contents}
    \label{fig:vts}
\end{figure}

\subsubsection{Vesicle budding} The process of vesicle budding involves sorting and packaging of cargo molecules, membrane deformation and budding of the vesicle from the source compartment (Fig.~\ref{fig:vts}).
%
Cargo sorting is performed by cytosolic adaptor proteins. 
Adaptors are recruited to the source compartment through interactions with the lipids that form the compartment's membrane, and interactions with molecular switches called Arf/Sar which signal the initiation of vesicle formation~\cite{paczkowski2015cargo}. 
%
Then these adaptors bind to cargo molecules and thereby sequester them for packaging. 
%
Different adaptor proteins act at different compartments, for example, vesicle formation at the ER requires the adaptor sec23/24, and the AP2 adaptor is used for packaging vesicles at the plasma membrane.
%

@@

\subsubsection{Vesicle fusion} The process of vesicle fusion involves two steps recognition of the correct target compartment and fusion of the transport vesicle (Fig.~\ref{fig:vts}).

@@

%\somya{schematic of intracellular compartments and  major routes}
\subsubsection{Major paths in the VTS}
Molecules traverse the cell in a series of vesicles, and there are two major routes of vesicle transport in all eukaryotic cells.
%
\begin{itemize}
	\item The secretory route takes proteins from the ER (their site of production) to the plasma membrane (from where they are secreted out of the cell) via the Golgi apparatus~\cite{alberts2002molecular}.
	%
	\item The endocytic route takes proteins from the outside of the cell, through the plasma membrane, to the endocytic compartments and the lysosome where they are digested. 
\end{itemize}
Other paths are used for cross talk between the secretory and the endocytic routes. For example, vesicles are sent back and forth between the Trans-Golgi network (secretory route) to the early and the late endosomes (endocytic route)~\cite{progida2016bidirectional}. Also, recently, unconventional vesicle-mediated secretory routes have been found, which bypass the Golgi apparatus. The molecules involved in these routes are as yet unknown~\cite{nickel2018unconventional}. 
%
%\begin{table}
%	\begin{center}
%		\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
%			\hline
%			Nodes & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 \\ \hline
%			Graphs & 0 & 0 & 0 & 1 & 2 & 15 & 121 & 2159 & 68715 & 3952378 \\ 
%			\hline
%		\end{tabular}
%		\label{tab:threec}
%		\caption{Number of simple 3-edge-connected unlabelled N-node graphs.}
%	\end{center}	
%\end{table}

@@

%\ankit{We need not specify Synthesis here. Only connectivity use next subsection to build this.}
%\somya{But this is the para where we explain why connectivity is interesting an biological property}
%\ankit{Yes; Both of our remark looks correct!}
The vesicle transport graphs available today for eukaryotic organisms are incomplete themselves. 
%
In this situation, we use our result as a tool to predict missing edges which satisfy the graph connectivity constraint. 
%
These predictions are intended to be used as guides for future experiments. 
%
A mismatch between our predictions and experiments would indicate that our current understanding of the VTS molecules is necessarily incomplete. 
%
Note that, on the other hand, if our predictions are experimentally confirmed, it does not imply that our understanding of the VTS is complete.\\
%
%\begin{table}[!t]
%	\caption{Table Caption}
%	\label{tab1}
%	\centering
%	{\setlength\tabcolsep{0.1pt}%
%		\begin{tabular}{ccccccccccccccc}
%			& $D_1$ & $D_2$ & $D_3$ & $D_4$ & $D_5$ & $D_6$ && & $D_1$ & $D_2$ & $D_3$ & $D_4$ & $D_5$ & $D_6$ \\
%			$D_1$ & & \cca{0} & \cca{0} & \cca{0} & \cca{2} & \cca{0} && $D_1$ && \cca{0} & \cca{0} & \cca{2} & \cca{2} & \cca{2} \\
%			$D_2$ & \cca{0} & & \cca{2} & \cca{0} & \cca{2} & \cca{0} && $D_2$ & \cca{0} &  & \cca{3} & \cca{0} & \cca{0} & \cca{2} \\
%			$D_3$ & \cca{7} & \cca{4} &  & \cca{3} & \cca{0} & \cca{4} && $D_3$ & \cca{0} & \cca{4} &  & \cca{4} & \cca{2} & \cca{0} \\
%			$D_4$ & \cca{3} & \cca{0} & \cca{7} &  & \cca{4} & \cca{0} && $D_4$ & \cca{0} & \cca{0} & \cca{5} &  & \cca{0} & \cca{0} \\
%			$D_5$ & \cca{3} & \cca{7} & \cca{7} & \cca{2} &  & \cca{4} && $D_5$ & \cca{2} & \cca{2} & \cca{0} & \cca{4} &  & \cca{4} \\
%			$D_6$ & \cca{2} & \cca{2} & \cca{7} & \cca{2} & \cca{6} &  && $D_6$ & \cca{2} & \cca{2} & \cca{3} & \cca{0} & \cca{4} & \\
%	\end{tabular}}
%\end{table}
%
\input{fig2}
%
\begin{example}
%
In Fig.~\ref{fig:M1}, we present a VTS that has 2 compartments and 18 molecules with its corresponding pairing matrix.
%
%Molecules are represented as $Q_{i}$'s or $R_{i}$'s to make a clear distinction between Q and R SNAREs.
%
In the VTS, labels are a string of molecule, where we show active molecules in red color.
%
The activity of the molecules on the node is controlled
by the presence of the other molecules (exact Boolean function is not shown). 
%
The activity of the molecules on an edge is determined by the corresponding pairing matrix.
%
Note that molecules $X$ and $Y$ do not take part in the fusion but determine the activity of molecules at the corresponding nodes.
%
Below the VTS, we show the pairing matrix.
%
Rows in the matrix correspond to the labels of edges, and columns correspond to the labels of nodes.
%
An entry 1 represents pairing between molecules and 0 represents no pairing.
%
Every molecule flows on a cycle, ensuring steady state.
%
This is a 4-connected graph.
\end{example}
%
%\subsection{Modeling and Symbolic Analysis of VTS: An Overview}
\label{subsec:graphmodel}
%
\subsection{Combinatorial problem and use of Formal methods}
\noindent The analysis of VTS is a difficult problem
because of the combinatorial scaling of possible traffic topologies and regulatory rules. 
%
%For example, we might want to check some conjecture of interest for all graphs of a certain structure. 
%
%If the analysis is done on a large number of graphs, the joined effect of large quantity of graphs and combinatorially many possible regulatory rules will be difficult to handle by any tool.
If the analysis is done on a large number of graphs, the joined effect of this with combinatorially many possible regulatory rules will be difficult to handle by any tool.
%
Precise analysis of the properties of the VTS would be hindered for the same reason.

@@

\subsubsection{Size of the VTS system}
%Let us discuss the rough sizes of the system and expected behaviors.
%%
%A typical VTS may have about 10 compartments.
%%
%%Across eukaryotes, there are 20 broad SNARE varieties, though individual species can
%%contain higher numbers (humans have 41)~\cite{kloepper2007elaborate}..
%%
%The VTS may transport a large number of molecules but the molecules that
%are relevant of the control of VTS are about 50~\cite{kloepper2007elaborate}.
%%
%According to the definition the activity of molecules can be controlled by
%the presence of all other molecules.
%%
%However, in practice the activity of a molecule is controlled by
%the presence of ~2-3 other molecules.
A typical eukaryotic cell contains 9 organelles; the ER, the cis-, medial- and trans-Golgi, the early, late and recycling endosomes, the lysosome and the plasma membrane~\cite{lodish2008molecular}. 
%
The organellar content of cells varies across different organisms, for example, parasitic cells such as Trypanosomes have specialized secretory organelles called rhoptries and micronemes~\cite{gubbels2012evolution}. 
%
The organellar content may also vary across different states of the same cell, for e.g., during cell division, the Golgi apparatus disintegrates into vesicles~\cite{tang2013cell}. 
%
Also, across different cell-types, these organelles may be more or less differentiated, for example, the number of stacks in the Golgi varies across different cells~\cite{polishchuk2004structural}. 
%

@@

% i.e., formally as a boolean function that given requisite labels of nodes and vesicles that returns true if the required regulations are met. 
%
%
% Note that the formulas define among other things constraints over
% paths between nodes in the graph model of VTS. Similarly, one can
% define fusion rules as constraints over the boolean functions modeling
% the regulations.  
% For example, the steady state condition, described informally earlier, can be defined by the formula shown in Listing~1.1.
%\begin{itemize}
%\item \srivas{Detailed BIO to Graph problem}
%\end{itemize}
%Given definitions of fusion and budding rules and the steady state conditions, whether a VTS meets maximum connectivity requirement, i.e. the LGC property, can be verified by checking if the formula show in Listing~1.2 is valid.  Here we have defined the property by checking over existence of any fusion/budding rules.  We can eliminate the existential quantifier if we are interested in checking the property for a particular fusion/budding rule.
%
%\subsection{Converting the Graph Problem into Boolean SAT problem}
%\label{subsec:satproblem}
%To convert the graph problem described in sec~\ref{subsec:graphmodeling}, into a boolean SAT problem, we need to define a scheme to represent graphs and boolean functions using a suitable set of propositional variables.  In our earlier work, we modeled the graph problem in C using arrays to model graphs and boolean function.  We then used the CBMC model checker to convert the graph problem into a SAT problem.  One of the challenges we had in our earlier work is dealing with quantifiers.  Note that the connectedness property defined in Listing~1.2 has quantifier alternation.  Even if we were to eliminate the existential quantifier by instantiating the problem for a fixed set of fusion rules, we would have embedded quantifiers in the antecedent of implications.   CBMC supports only a quantifier-free logic n its assertion language.  In our earlier work we used a combination of explicit enumeration at the C-level and clever use f non-determinism to eliminate alternation of quantifiers.  This enumeration was one source of bottleneck for scaling in our earlier work.  In the current work we eliminate this bottleneck by modeling the problem directly as a SAT instance using uninterpreted functions and recursive relations.  The details of te hnew encding will described in subsequent sections.
%A VTS is {\em $k$-connected} if every pair of compartments remain reachable after dropping $k-1$ vesicles.
%
%This property of VTSs has been considered informative and studied by~\cite{shukla}.
%
%Here we have build an {\em efficient} tool that studies properties of VTSs that are not $k$-connected, from some $k$. 
\subsection{Synthesis of VTS }
\noindent The current picture of the VTS is far from complete; we do not yet know how many of the cellular proteins reach their resident compartments within the cell, and new vesicle routes are being discovered every year~\cite{nickel2018unconventional,weill2018toolbox}. 
%
Completing the VTS is a difficult task for many important reasons: 
\begin{enumerate}
    \item The core VTS is conserved across eukaryotes, the traffic network in different organisms \cite{richardson2015evolutionary, barlow2017seeing}, and even in different cell types within an organism can be different~\cite{stoops2014trafficking,zhou2015arp2}.

@@

    \item Molecules can have redundant routes within the cell~\cite{shimizu2014compensatory,nakatsukasa2014nutrient}.
    \item Behaviour of traffic molecules in vitro is different from their behavior inside cells~\cite{furukawa2014multiple}. 
    \item It can be difficult to distinguish between the direct and indirect effects of experiments involving knock-downs or knockouts of traffic molecules \cite{hirst2004epsinr,mishev2013small}.
\end{enumerate}

Nonetheless, completing the VTS for different organisms is very useful. 
%
Many diseases are caused by the malfunction of the VTS. 
%
Knowledge of the complete network would be helpful in identifying the root causes of ~\cite{bexiga2013human,gissen2007cargos}. 
%
At a more basic level, having complete pictures of the VTS for various organisms and various cell-types would allow comparative studies, and therefore would allow the deduction of modes of evolution of the form of the traffic network. 
%
This would also allow us to decipher features such as parts of the traffic system that is unchanging, and therefore likely to be its core, and parts that are more plastic \cite{barlow2017seeing}.

%\subsection{Synthesis of VTS:}
%
The set of basic constraints the VTS should follow is dictated by underlying cell biology.   
%
In order to attempt to complete a given partial VTS, we have to first agree on the properties that every complete VTS should follow in spite of the basic constraints. 
%
We can use our stability and k-connectivity constraints as a basis for this investigation.   
%
The incomplete VTS might not respect these constraints. 
%
In this paper, using constraints on global vesicle traffic network topology due to local molecular interactions, we take incomplete pictures of vesicle traffic networks as inputs.
%
We output various completed versions of VTS against these properties which can then be tested experimentally.
%
\input{fig3}
\begin{example}
    In Fig.~\ref{fig:synth-vts1}, we present a partial input VTS that has 3 compartments. Fig.~\ref{fig:synth-vts2} present it's complete output VTS. Every molecule present on the node is active. The activity of the molecules on an edge is determined by the presence of the other molecules. Each label represent particular type of molecule. The synthesis is performed against the stability and 3-connectivity. Synthesized edge is in red color and synthesized molecules are presented in blue. The synthesis adds one edge and 7 molecules to complete the partial VTS. For the sake of clarity, we have not presented the activity of molecules, the corresponding pairing matrix and remaining molecules on the nodes.
\end{example}
%
We have implemented the encoding in a flexible tool, which can handle a wide range of synthesis queries. 
%
We have applied our tool on several VTSs including
two found-in-nature VTSs.
%
Our experiments suggest that some of the synthesis problems are solvable by modern solvers and the synthesis technology may be useful for biological research.
%

### 2019-06-15 papers/journal/prelim.tex
First Update for revision

\noindent We will use lower case variables like $e,r,s$, etc to represent vectors of
Boolean variables, possibly indexed, with multiple dimensions.
%
For example, $r_{ij}$ is a Boolean variable for index $(i,j)$.
%
%
A Boolean variable may take Boolean values $1$ or $0$.
%
The binary Boolean operators $\land$, $\lor$, and $\limplies$ are usually defined.
%
$\Land$ and $\Lor$ are operators that extend $\land$ and $\lor$ over a collection of formulas respectively.
%
We will use the variables and operators to construct Boolean formulas to
encode our problems.
%
An assignment is a map from the variables in the formula to the Boolean values.
%
An assignment may satisfy a formula if the interpretation of Boolean operators
reduces the whole Formula into 1.
%
The problem of finding a satisfying assignment for a Boolean formula is known to be hard~\cite{cook1971complexity}.
%

Quantified Boolean formulas(QBFs) also allow quantifiers over Boolean variables.
%
For example, $\forall x \exists y. (x \lor y)$, for Boolean variables $x$ and $y$.
%
The formula says that for both the values of $x$ there is a value of $y$
such that $x \lor y$ is 1.
%
The problem of finding a satisfying assignment for QBFs is even harder problem~\cite{stockmeyer1973word, arora2009computational}.\\
%

\subsubsection{Solvers}
In this paper, we will encode several problems into finding satisfying
solutions of a Boolean formula or QBFs.
%
We will use BMC, SMT and QBF solvers to get the satisfying assignments.
%
The modern solvers are the result of several decades of research
and implement sophisticated algorithms.
%
A SAT solver typically implements conflict-driven clause learning (CDCL)~\cite{biere2009conflict}.
%1
The QBF solver adds support of quantifiers by adding more rules for quantifiers~\cite{buning2009theory}.

>>>>

\noindent We will use lower case variables like $e$, $r$, $s$, etc to represent vectors of
Boolean variables, possibly indexed, with multiple dimensions.
%
For example, $r_{ij}$ is a Boolean variable for index $(i,j)$.
%
%
A Boolean variable may take Boolean values $1$ or $0$.
%
The binary Boolean operators $\land$, $\lor$, and $\limplies$ are usually defined.
%
$\Land$ and $\Lor$ are operators that extend $\land$ and $\lor$ over a collection of formulas respectively.
%
We will use the variables and operators to construct Boolean formulas to
encode our problems.
%
An assignment is a map from the variables in the formula to the Boolean values.
%
An assignment may satisfy a formula if the interpretation of Boolean operators
reduces the whole Formula into 1.
%
The problem of finding a satisfying assignment for a Boolean formula is known to be hard~\cite{cook1971complexity}.
%

QBFs also allow quantifiers over Boolean variables.
%
For example, $\forall x \exists y. (x \lor y)$, for Boolean variables $x$ and $y$.
%
The formula says that for both the values of $x$ there is a value of $y$
such that $x \lor y$ is 1.
%
The problem of finding a satisfying assignment for QBFs is even harder problem~\cite{savitch1970relationships, stockmeyer1973word}.
%

\subsubsection{Solvers}
In this paper, we will encode several problems into finding satisfying
solutions of a Boolean formula or QBFs.
%
We will use SAT, SMT and QBF solvers to get the satisfying assignments.
%
The modern solvers are the result of several decades of research
and implement sophisticated algorithms.
%
A SAT solver typically implements conflict-driven clause learning (CDCL)~\cite{biere2009conflict}.
%1
The QBF solver adds support of quantifiers by adding more rules for quantifiers~\cite{buning2009theory}.
